%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume (Jake's Resume Template)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

\titlespacing{\section}{0pt}{10pt}{6pt}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=6pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=1pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Harsh Kumar} \\ \vspace{3pt}
    \small +91-6200230016 $|$
    \href{mailto:harshkr1624@gmail.com}{\underline{harshkr1624@gmail.com}} $|$
    \href{https://github.com/harshsync}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/harsh-kumar-619453307}{\underline{LinkedIn}} $|$
    \href{https://codeforces.com/profile/harsh1624}{\underline{Codeforces}}
\end{center}


%-----------SUMMARY-----------
\section{Professional Summary}
    \small{Computer Science undergraduate with hands-on experience developing backend applications using Java, Spring Boot, Hibernate ORM, PostgreSQL, and MySQL. Strong foundation in Object-Oriented Programming, DBMS, REST APIs, and Data Structures.}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, SQL, Python (Basic)} \\[2pt]
     \textbf{Frameworks}{: Spring Boot, Spring MVC, Spring Core, Spring Data JPA, Hibernate ORM} \\[2pt]
     \textbf{Databases}{: PostgreSQL, MySQL} \\[2pt]
     \textbf{Build Tools}{: Maven} \\[2pt]
     \textbf{Technologies}{: REST APIs, JDBC} \\[2pt]
     \textbf{Developer Tools}{: Git, GitHub, IntelliJ IDEA, Postman, DBeaver} \\[2pt]
     \textbf{Core CS}{: OOP, Collections Framework, DBMS, Operating Systems, Computer Networks, Data Structures \& Algorithms}
    }}
 \end{itemize}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Complaint Management System} $|$ \emph{Java, Spring Boot, Spring Data JPA, MySQL, Maven}}{In Progress}
          \resumeItemListStart
            \resumeItem{Developing a backend Complaint Management System using Spring Boot following the Controller--Service--Repository architecture.}
            \resumeItem{Built REST APIs for complaint registration, status updates, assignment, and retrieval using Spring MVC.}
            \resumeItem{Integrated MySQL with Spring Data JPA and implemented CRUD operations with request validation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Student Course Registration System} $|$ \emph{Java, Hibernate ORM, PostgreSQL, Maven}}{June 2026}
          \resumeItemListStart
            \resumeItem{Developed a console-based Student Course Registration System using Java, Hibernate ORM, PostgreSQL, and Maven.}
            \resumeItem{Implemented CRUD operations, DAO architecture, Hibernate Transactions, and HQL queries for database management.}
            \resumeItem{Implemented Hibernate Many-to-Many mapping for Student-Course enrollment with input validation and menu-driven navigation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Competitive Programming}{}
      {Codeforces}{}
      \resumeItemListStart
        \resumeItem{Achieved a maximum rating of \textbf{1261 (Pupil)} on Codeforces by solving algorithmic and data structure problems.}
        \resumeItem{\href{https://codeforces.com/profile/harsh1624}{\underline{Codeforces Profile}}}
      \resumeItemListEnd

    \resumeSubheading
      {Hackathon Finalist}{Jan 2026}
      {Data-U-Biz, MANIT Bhopal}{}
      \resumeItemListStart
        \resumeItem{Reached the Final Round of the Data-U-Biz Hackathon conducted by MANIT Bhopal.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VIT Bhopal University}{Madhya Pradesh}
      {B.Tech in Computer Science and Engineering -- CGPA: 8.01}{Sept 2023 -- Present}
    \resumeSubheading
      {Himalayan Residential School}{Bihar}
      {Class XII -- 76\%}{2022}
    \resumeSubheading
      {Don Bosco Academy}{Bihar}
      {Class X -- 92\%}{2020}
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, itemsep=2pt]
    \small{
      \item AWS Certified Solutions Architect -- Associate
      \item AWS Certified Cloud Practitioner (CLF-C02)
    }
 \end{itemize}


%-------------------------------------------
\end{document}